---
title: 'Subject 1001B: Demographics'
author: "Shuying Yu"
date: "7/13/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    theme: journal
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center")

#Attach packages
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
library(patchwork)
library(ggpubr)
library(RColorBrewer)
```


```{r clean_data}

########## ALL
data_all <- read_csv(here("data", "HAS_demo_all.csv")) %>% 
  clean_names()



########## CLEAN

#Read data and clean variable names
data <- read_csv(here("data", "HAS_demo_all.csv")) %>% 
  clean_names()

#Select certain columns just for review
data_sub <- data %>% 
  select(subject_id, sex, reproductive_status, age_scan_years,
        bmi, self_ses, education_years, verbal_iq, straw_10_stages,
        
        #Women's basic repro health
        age_at_menarche_years, time_since_last_cycle_years,
        menopausal_status,
        
        #TH and IP qualtrics
        edinburgh_handedness:ltpa_total,
        
        #Facename
        fname_nt, fname_ot, fname_t)

#Remove men from repo
data_sub_repo <- data_sub %>% 
  filter(reproductive_status != "Men") %>% 
  mutate(reproductive_status = fct_relevel(reproductive_status, 
                                         c("Pre", "Peri", "Post")))
```



# Introduction

Data of the *cleaned* sample of Healthy Aging Participants, meaning that these are participants that we have decided to include based on complete fMRI scans, no major health problems from demographic survey, and from previous team discussions of who to exclude as we wrapped up recruitment for the study.

Subjects ranged from 301-437, scanned over the course of March 1, 2017 to February 10, 2022.

Black diamond point are the group means. Highlighted in purple triangle point and purple line is subject 1001B.

Figures will only include basic demographic and neurpsychiatric batteries. Given little overlap between the type of neuropsychiatric assessments between the HAS sample and subject 1001B, more data pulled from the Reproductive Heath Questionnaire from the demographic survey will be included in this report.



# Basic Demographics {.tabset}

Age (years), BMI, highest completed level of education (years), and verbal IQ

**Age:** Ranges from 43-60 years old

**BMI:** Healthy adult BMI levels are about 19-25

**Education:**

- Some College or Associate's = 14 years

- Bachelor's = 16 years

- Master's = 18 years

- Doctoral = 20 years

**Verbal IQ:** Ranges from 74-132 based on AMNART scores


## Reproductive Status


```{r}
#Age
p1 <- ggplot(data = data_sub_repo, aes(y = age_scan_years,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Age (years)",
       title = "Age") +
  
  #Add 1001b
  geom_point(aes(x = factor("Post"), y=57),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#BMI
p2 <- ggplot(data = data_sub_repo, aes(y = bmi,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "BMI",
       title = "BMI") +
  
  #Add 1001b
  geom_point(aes(x = factor("Post"), y=21.45),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Education
p3 <- ggplot(data = data_sub_repo, aes(y = education_years,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Education (years)",
       title = "Education") +
  
  #Add 1001b
  geom_point(aes(x = factor("Post"), y=14),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Verbal IQ
p4 <- ggplot(data = data_sub_repo, aes(y = verbal_iq,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Verbal IQ",
       title = "Verbal IQ")

#Combine
(p1+p2)/(p3+p4)
```
Suject 438:

- Age: 64 years old

- BMI: 20.4

- Education: Master's degree (18 years of education)

Subject 1001B did not do AMNART for Verbal IQ.

## Sex

```{r}
#Age
p1 <- ggplot(data = data_sub, aes(y = age_scan_years,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Age (years)",
       title = "Age") +
    #Add 1001b
  geom_point(aes(x = factor("Female"), y=57),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#BMI
p2 <- ggplot(data = data_sub, aes(y = bmi,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "BMI",
       title = "BMI") +
    #Add 1001b
  geom_point(aes(x = factor("Female"), y=21.45),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Education
p3 <- ggplot(data = data_sub, aes(y = education_years,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Education (years)",
       title = "Education") +
    #Add 1001b
  geom_point(aes(x = factor("Female"), y=14),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Verbal IQ
p4 <- ggplot(data = data_sub, aes(y = verbal_iq,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Verbal IQ",
       title = "Verbal IQ")

#Combine
(p1+p2)/(p3+p4)
```


## Total

```{r}
#Age
p1 <- ggplot(data = data_sub, aes(x = age_scan_years)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Age (years)",
       y = "Count",
       title = "Age") +
  #Add 1001b
  geom_vline(aes(xintercept = 57), color = "purple", size = 1.5)


#BMI
p2 <- ggplot(data = data_sub, aes(x = bmi)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "BMI",
       y = "Count",
       title = "BMI") +
  #Add 1001b
  geom_vline(aes(xintercept = 21.45), color = "purple", size = 1.5)


#Education
p3 <- ggplot(data = data_sub, aes(x = education_years)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Education (years)",
       y = "Count",
       title = "Education") +
  #Add 1001b
  geom_vline(aes(xintercept = 14), color = "purple", size = 1.5)


#Verbal IQ
p4 <- ggplot(data = data_sub, aes(x = verbal_iq)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Verbal IQ",
       y = "Count",
       title = "Verbal IQ")

#Combine
(p1 + p2)/(p3 + p4)
```


#  {-}

<br>


# Reproductive Health Characteristics {.tabset}

 
Women only. Includes only age at menarche (years) and time since last menstrual cycle (years).


```{r table-age-straw10-clean}
tab_age_straw <- data_sub_repo %>% group_by(reproductive_status,
                                            straw_10_stages) %>% 
  
    drop_na() %>% 
    summarise(count = n(),
            mean_age = mean(age_scan_years),
            sd_age = sd(age_scan_years),
            min_age = min(age_scan_years),
            max_age = max(age_scan_years))

tab_age_straw %>% 
  kable(col.names = c("Reproductive Status", "Straw-10 Stages",
                      "Count", "Mean Age (years)", 
                      "Standard Deviation of Age (years)",
                      "Minimum Age (years)", "Maximum Age (years)"),
        
        #Add caption
        caption = "Age characteristics of clean HAS sample of women, by reproductive stages.",
        
        #Align all cells/columns to center
        align = c(rep("c", times = 7)),
        
        #Round digits to 2
        digits = 2) %>%
  
  #Make full width and add hover to rows
  kable_styling(full_width = TRUE,
                position = "center",
                bootstrap_options = "hover")
```


## Reproductive Status

```{r}
#Age at menarche
p1 <- ggplot(data = data_sub_repo, aes(y = age_at_menarche_years,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Age (years)",
       title = "Age at Menarche") +
  #Add 1001b
  geom_point(aes(x = factor("Post"), y=15),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Time since last cycle 
p2 <- ggplot(data = data_sub_repo, aes(y = time_since_last_cycle_years,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Time (years)",
       title = "Time Since Last Menstrual Cycle")+
  #Add 1001b
  geom_point(aes(x = factor("Post"), y=2),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Combine
(p1+p2)
```


## Total

```{r}
#Age at menarche
p1 <- ggplot(data = data_sub, aes(x = age_at_menarche_years)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Age (years)",
       y = "Count",
       title = "Age at Menarche")+
  #Add 1001b
  geom_vline(aes(xintercept = 15), color = "purple", size = 1.5)


#Time since last cycle 
p2 <- ggplot(data = data_sub, aes(x = time_since_last_cycle_years)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Time (years)",
       y = "Count",
       title = "Time Since Last Menstrual Cycle")+
  #Add 1001b
  geom_vline(aes(xintercept = 2), color = "purple", size = 1.5)


#Combine
(p1+p2)
```


#  {-}

<br>

# Neuropsychiatric Assessments {.tabset}


## Edinburgh Handedness 

Measures handedness (most are right handed)

-	Score of -1.0		= Pure Left Hander

-	Score of -0.5		= Mixed Left Hander

-	Score of 0.0		= Neutral

-	Score of +0.5		= Mixed Right Hander

-	Score of +1.0		= Pure Right Hander

```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = edinburgh_handedness,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Handedness",
       title = "Reproductive Status") + 
  theme(legend.position = "none") +
   #Add 1001b
  geom_point(aes(x = factor("Post"), y=1),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Sex
p2 <- ggplot(data = data_sub, aes(y = edinburgh_handedness,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Handedness",
       title = "Sex") + 
  theme(legend.position = "none") +
      #Add 1001b
  geom_point(aes(x = factor("Female"), y=1),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)



#Total
p3 <- ggplot(data = data_sub, aes(x = edinburgh_handedness)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Handedness",
       y = "Count",
       title = "Total") +
  #Add 1001b
  geom_vline(aes(xintercept = 1), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```

Subject 1001B: score of 1.0 (pure right hander)


## Geriatric Depression

Measures participant depression

- Scores ranging 0-5 are considered normal

- Scores that are 5+ suggest depression

```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = geriatric_depression,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Geriatric Depression",
       title = "Reproductive Status") + 
  theme(legend.position = "none")+
   #Add 1001b
  geom_point(aes(x = factor("Post"), y=5),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Sex
p2 <- ggplot(data = data_sub, aes(y = geriatric_depression,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Geriatric Depression",
       title = "Sex") + 
  theme(legend.position = "none")+
   #Add 1001b
  geom_point(aes(x = factor("Female"), y=5),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = geriatric_depression)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Geriatric Depression",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 5), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```


Subject 1001B: score of 5


Scale was developed by Sheikh & Yesavage, 1986.



## PSQI

Pittsburgh Sleep Quality Index. Measures quality of sleep by taking into account 7 components: habitual sleep efficiency, subjective sleep quality, sleep duration, sleep latency, use of sleep medications, sleep disturbances, and daytime dysfunction.

Each component is given a score from 0-3, with 0 meaning no difficulty and 3 meaning having severe difficulty.

The PSQI score thus ranges from 0-21:

- Scores of 0 = No difficulty sleeping

- Score of 21 = Severe difficulties in all components/areas


```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = psqi,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "PSQI Score",
       title = "Reproductive Status") + 
  theme(legend.position = "none")+
   #Add 1001b
  geom_point(aes(x = factor("Post"), y=3),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Sex
p2 <- ggplot(data = data_sub, aes(y = psqi,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "PSQI Score",
       title = "Sex") + 
  theme(legend.position = "none")+
   #Add 1001b
  geom_point(aes(x = factor("Female"), y=3),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = psqi)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "PSQI Score",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 3), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```

Subject 1001b: score of 3



## STAI

State-Trait Inventory for Adults (STAI) measures participant’s anxiety

**STATE:** current level of anxiety


```{r stai-state}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = stai_state,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Current Anxiety Level",
       title = "Reproductive Status") + 
  theme(legend.position = "none") +
     #Add 1001b
  geom_point(aes(x = factor("Post"), y=20),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Sex
p2 <- ggplot(data = data_sub, aes(y = stai_state,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Current Anxiety Level",
       title = "Sex") + 
  theme(legend.position = "none")+
     #Add 1001b
  geom_point(aes(x = factor("Female"), y=20),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = stai_state)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Current Anxiety Level",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 20), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```


Subject 1001B: score of 20 (for state only)



# {-}

<br>

# {-}

# Face Name Memory {.tabset}


## Name Learning and Retrieval

Name Learning & Retrieving Composite of:

- Initial recall of names (1st and 2nd rounds)

- Cued recall of names after 2 trials


```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = fname_nt,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Names Total",
       title = "Reproductive Status") + 
  theme(legend.position = "none") +
     #Add 1001b
  geom_point(aes(x = factor("Post"), y=13),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Sex
p2 <- ggplot(data = data_sub, aes(y = fname_nt,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Names Total",
       title = "Sex") + 
  theme(legend.position = "none") +    #Add 1001b
  geom_point(aes(x = factor("Female"), y=13),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = fname_nt)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Names Total",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 13), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```


Subject 1001B: score of 13

## Occupation Learning and Retrieval

Occupation Learning & Retrieving Composite

- Initial recall of occupations (1st and 2nd rounds)

- Cued recall of occupations after 2 trials


```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = fname_ot,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Occupation Total",
       title = "Reproductive Status") + 
  theme(legend.position = "none")+
     #Add 1001b
  geom_point(aes(x = factor("Post"), y=24),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)



#Sex
p2 <- ggplot(data = data_sub, aes(y = fname_ot,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Occupation Total",
       title = "Sex") + 
  theme(legend.position = "none")+    #Add 1001b
  geom_point(aes(x = factor("Female"), y=24),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = fname_ot)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Occupation Total",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 24), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```


Subject 1001B: score of 24

## Composite Name and Occupation

Composite of Name and Occupation Learning and Recall (Total)

Sum of FNAME-NT and FNAME OT


```{r}
#Reproductive status
p1 <- ggplot(data = data_sub_repo, aes(y = fname_t,
                                 x = reproductive_status,
                                 fill = reproductive_status,
                                 color = reproductive_status)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Reproductive Status",
       y = "Face Name Total",
       title = "Reproductive Status") + 
  theme(legend.position = "none")+
     #Add 1001b
  geom_point(aes(x = factor("Post"), y=37),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)



#Sex
p2 <- ggplot(data = data_sub, aes(y = fname_t,
                                 x = sex,
                                 fill = sex,
                                 color = sex)) + 
  geom_boxplot(alpha = 0.5,show.legend = FALSE) +
  geom_jitter(width = 0.1, show.legend = FALSE) +
  stat_summary(fun.y=mean, geom="point",
               shape=20, size=3, color="black", fill="black") +
  labs(x = "Sex",
       y = "Face Name Total",
       title = "Sex") + 
  theme(legend.position = "none")+    #Add 1001b
  geom_point(aes(x = factor("Female"), y=37),
             color = "purple", shape = 17, size = 3,
             show.legend = FALSE)


#Total
p3 <- ggplot(data = data_sub, aes(x = fname_t)) + 
  geom_histogram(alpha = 0.5, position = "identity",
                 show.legend = FALSE) +
  labs(x = "Face Name Total",
       y = "Count",
       title = "Total")+
    #Add 1001b
  geom_vline(aes(xintercept = 37), color = "purple", size = 1.5)

#Combine
(p1+p2)/p3
```


Subject 1001B: score of 37

# {-}







